cover letter

### 2022-11-22 paper/admin/cover_letter.tex

 At the other end of this continuum, ``heavyweight'' approaches entail
 simulating or replicating, to varying depths, the original computing
 environment in which the shared code was developed.  For example,
 virtual environments, containerized systems, and virtual machines
 reproduce (respectively) a complete Python environment, operating system, and/or
 full hardware simulation of the original environment.  Each of these
 systems guarantees, to varying degrees, that shared code will behave
 as expected for the end user.  A downside to these approaches is that
 they are often effort- and/or resource-intensive, since they require
 installing and mastering additional tools (e.g., Anaconda, Docker, machine
 emulators, etc.), as well as writing and distributing additional
 configuration files (e.g., environment configuration files,
 Dockerfiles, system images, etc.), in order to share and run reproducible code.

>>>>

 At the other end of this continuum, ``heavyweight'' approaches entail
 simulating or replicating, to varying depths, the original computing
 environment in which the shared code was developed.  For example,
 virtual environments, containerized systems, and virtual machines
 reproduce (respectively) a complete Python environment, operating system, and/or
 full hardware simulation of the original environment.  Each of these
 systems guarantees, to varying degrees, that shared code will behave
 as expected for the end user.  A downside to these approaches is that
 they are often effort- and/or resource-intensive, since they require
 installing and learning additional tools (e.g., Anaconda, Docker, machine
 emulators, etc.), as well as writing and distributing additional
 configuration files (e.g., environment configuration files,
 Dockerfiles, system images, etc.), in order to share and run reproducible code.
